### 2017-08-30 status.tex
added a caveat that the exponent should be greater than zero and changed notation

Equations \eqref{eq:error} - \eqref{eq:size} define the block size model. To complete this model we must specify the intensity function, $\psi(u)$, and priors for all of the unknown parameters. In the original version of the paper we only considered a constant intensity $\psi(u) = \gamma > 0$, though we can also define an increasing intensity $\psi(u) = e^{\beta_0 + u\beta_1}$. In principle we can define any intensity function of the form $\psi(u) = e^{\bm{z}(u)'\bm{\beta}}$ where $\bm{z}(u)$ is a vector of basis functions of time, and $\bm{\beta}$ is a vector of regression coefficients. However, we need to be able to compute the integral $\int_{\tau}^{\tau + \delta}\psi(u)du$ in closed form, which restricts the form of $\psi(u)$. One possibility that I have not explored that may be more flexible is $\psi(u) = \sum_{p=1}^P\alpha_pu^{\beta_p - 1}$ with $\alpha_p, \beta_p\geq 0$ for $p=1,2,\dots,P$. In this case, then $\Psi(\tau) = \int_0^\tau\psi(u)du = \alpha_p\tau^{\beta_p}/\beta_p$ where $\tau^0/0$ is defined to be $\log(\tau)$. If $\beta_p < 1$ then the $p$th term of $\psi(u)$ decays in $u$, while if $\beta_p > 1$ it increases in $u$ and if $\beta_p = 1$ it is constant in $u$.

>>>>

Equations \eqref{eq:error} - \eqref{eq:size} define the block size model. To complete this model we must specify the intensity function, $\psi(u)$, and priors for all of the unknown parameters. In the original version of the paper we only considered a constant intensity $\psi(u) = \gamma > 0$, though we can also define an increasing intensity $\psi(u) = e^{\beta_0 + u\beta_1}$. In principle we can define any intensity function of the form $\psi(u) = e^{\bm{z}(u)'\bm{\beta}}$ where $\bm{z}(u)$ is a vector of basis functions of time, and $\bm{\beta}$ is a vector of regression coefficients. However, we need to be able to compute the integral $\int_{\tau}^{\tau + \delta}\psi(u)du$ in closed form, which restricts the form of $\psi(u)$. One possibility that I have not explored that may be more flexible is $\psi(u) = \sum_{p=1}^P\beta_pu^{\alpha_p - 1}$ with $\alpha_p, \beta_p\geq 0$ for $p=1,2,\dots,P$. In this case, then $\Psi(\tau) = \int_0^\tau\psi(u)du = \beta_p\tau^{\alpha_p}/\beta_p$. If $\alpha_p < 1$ then the $p$th term of $\psi(u)$ decays in $u$, while if $\alpha_p > 1$ it increases in $u$ and if $\alpha_p = 1$ it is constant in $u$. Strictly speaking we require $\alpha_p > 0$ since if $\alpha_p = 0$ then $\Psi(0) = -\infty$, while if $\alpha_p > 0$ then $\Psi(0) = 0$, which is what we require.
